First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-02 eg6-letters/coherent/dvcs_he4_prl.tex
Edition of letter in progress and file clean up

A wealth of information on the quantum chromodynamics (QCD) lies in the 
internal structure of hadrons. In the recent past, the development of the 
generalized parton distributions (GPDs) framework has offered the possibility
to obtain new information about the momentum and spatial degrees of 
freedom of the quark and gluons inside hadrons [Add ref Mueller, Ji, Rad.]. 
In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
transverse plane for partons carrying a certain longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep}.

The main access to GPDs is through the measurement of deep virtual Compton 
scattering (DVCS), i.e. the hard exclusive electroproduction of a real photon. 
While other processes are known to be sensitive to GPDs, the measurement of the
DVCS is considered as the cleanest probe and has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
[Should we cite less publications on the topic or a review?]
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN. The vast majority of these measurements was focused on the study of the 
proton structure and allow the extraction of the tomography of the nucleon [refs].
This framework is also applicable to nuclei, giving access to completely new 
information about the nuclear structure in terms of quarks and gluons[refs to add].
The study of the 3D structure of the nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions [ref to EMC reviews].

@@

%DVCS selection
To identify the coherent DVCS events, we first select events where one 
electron, one $^4$He and at least one photon are detected in the final state. 
Electrons are identified by using fiducial cuts and detecting a good
signals in all the sub-detectors of the base line CLAS (drift chambers, 
Cherenkov counters, electromagnetic calorimeter, and time of flight 
scintillators). The $^4$He tracks are identified with fiducial, 
timing and track quality cuts in the RTPC detector. In addition,
we apply a vertex matching cut to make sure the electron and the helium
nuclei originate from the same place. The photons are detected either
in the IC or the CLAS electromagnetic calorimeter, note that even though the 
DVCS reaction has only one real photon in the final state, 
events with more than one good photon are not discarded at this stage. This is 
motivated by the fact that soft photons are likely to be produced in random 
coincidences, but cannot be mistaken for DVCS photons which are always at high
energies ($>2$ GeV).

Then, events with one or 
more $\pi^{0}$ are removed from the coherent DVCS sample. After that, the most 
energetic IC photon was considered as the DVCS photon candidate. Next, a 
$Q^{2}>1~[GeV^{2}/c^{2}]$ cut is applied on the DVCS candidates in order to 
ensure that the interaction occurs at the partonic level and the applicability 
of the factorization in the DVCS handbag diagram.  Once the three final state 
particles were identified with their 3-momentum vectors, the exclusivity of the 
coherent DVCS events were ensured by applying a set of exclusive cuts, which 
are: the co-planarity angle ($\Delta \phi$), missing energy, missing mass 
squared and missing transverse momentum in the $e'^4He'\gamma X$ final state 
configuration, the missing mass squared in the $e'^4He'X$ and $e'\gamma X$ 
configurations, and finally the cone angle ($\theta$) between the measured real 
photon and the missing particle in the $e'^4He'X$ configuration.  
Figure~\ref{fig:kin-cuts} presents four of the applied exclusivity cuts, where 
3$\sigma$ cuts are applied on all the exclusive quantities except the missing 
energy, for which a [-0.45,0.5] GeV cut was adopted to reduce the background 
contribution. Finally,

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
\caption{Four of the seven coherent DVCS exclusivity cuts. The black 
distributions represent the coherent DVCS events candidate. The shaded 
distributions represent the events which passed all the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied exclusivity 
cuts. The distributions from left to right and from top to bottoms are: $\Delta 
\phi$, missing energy and missing mass squared in $e'^4He'\gamma X$, and the 
cone angle ($\theta$) between the measured and the calculated photons.}
\label{fig:kin-cuts}
\end{figure}
After all the requirements on the individual final state particles of the 
coherent DVCS events and the exclusivity cuts, we ended up with about 3500 
events. Figure \ref{fig:kin-coverage} presents the ($Q^{2}$,$x_{B}$) and 
($Q^{2}$,$-t$) kinematic coverage of the collected DVCS events.

\begin{figure}[tb]
\hspace{-0.45cm}
\includegraphics[width=9.0cm]{figs/Q2_xB_t_Coh.pdf}
\caption{The $Q^{2}$ as a function of $x_{B}$ (left) and the $Q^{2}$ as a 
function of $-t$ (right) for the identified coherent DVCS events after the 
exclusivity cuts.}
\label{fig:kin-coverage}
\end{figure}

Even with all the previously presented exclusive cuts, the selected events are
not all true DVCS events. We identified several background contributions to the 
coherent DVCS process, in particular accidental events and exclusive Deeply 
Virtual $\pi^0$ Production (DV$\pi^0$P). The accidental events where the 
different particles come from different events are suppressed by the limited 
phase space allowed by the exclusivity cuts. We estimate the accidental events 
to represent 4.1\% of our sample. This relatively large number is due to the 
small cross section of the DVCS. We evaluated this contribution by selecting 
events passing all our cuts but with particles originating from different 
vertices. Regarding the DV$\pi^0$P, which can easily be mistaken with DVCS when 
one of the two photons of the $\pi^0$ decay is produced at low energy in the 
laboratory frame. To estimate the importance of this background, we developed 
an event generator that we calibrated to match our measured experimental yield 
of exclusive $\pi^0$. We used this generator together with a GEANT3 simulation 
of our detection system to estimate the ratio of acceptance between DV$\pi^0$P 
where the two photons are detected and those where only one photon is detected 
and would pass our DVCS selection cuts. This ratio obtained from simulation is 
then multiplied by the measured yield of DV$\pi^0$P events, indicating a 
contamination of 2 to 4\%. The study of systematics errors showed that the main 
contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
large binning size (5.1\%). However added quadratically, these errors sum up to 
10\%, which remain for all bins well below the statistical errors.

%asymmetries
Different observables are available in DVCS, the cross sections, the BSA...
This work presents the first exclusive measurement of the beam-spin asymmetry 
of the reaction $e~^{4}He\rightarrow e'~^{4}He~\gamma$. This DVCS sensitive 
observable is measurable using a polarized lepton beam on an unpolarized target 
(U). It is convenient to use the beam-spin asymmetry as a DVCS observable 
because most of the experimental normalization and acceptance issues cancel out 
in the asymmetry ratio. It is defined in terms of the cross sections as:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross 
section for a positive (negative) beam helicity. Experimentally, the DVCS 
reaction is indistinguishable from the Bethe-Heitler (BH) process, where the 
final photon is emitted either from the incoming or the outgoing leptons. The 
BH process is not sensitive to GPDs and does not carry information about the 
partonic structure of the hadronic target, and it's amplitude is calculable 
from the well-known electromagnetic form factors.

At leading twist order, the photon-electroproduction cross section can be 
decomposed into a BH, a DVCS, and an interference terms. The amplitudes of the 
three terms is approximated as a finite sum of Fourier harmonics, the so-called 
BMK approximation, as shown for the nucleon DVCS in \cite{Belitsky:2001ns} and 
for the spinless nuclei in \cite{Kirchner:2003wt,Belitsky:2008bz}. Therefore, 
the beam-spin asymmetry ($A_{LU}$) with the two opposite helicities of a 
longitudinally-polarized electron beam (L) on a spin-zero target (U) can be 
simplified as:
\small
\begin{equation}
\begin{split}
A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
 \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
\label{eq:A_LU-coh}
\end{split}
\end{equation}
\normalsize
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$. 
$\phi$ is the azimuthal angle between the ($e$,$e'$) and 
($\gamma^{*}$,$^4$He$'$) planes. The $\alpha_{i}$'s are $\phi$-dependent 
kinematical factors that depend on the nuclear form factor ($F_{A}(t)$) and the 
independent variables $Q^2$, $x_{B}$ and $t$. These factors are simplified as:
\small
\begin{eqnarray}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2}
\end{eqnarray}
\normalsize

Where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$ is the $^4$He mass, 
$\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the Bethe-Heitler
propagators. The factors: $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and
$s_1^{INT}$ are the Fourier coefficients of the BH, $S{++}(1)$, $C_{++}(0)$, 
and $C_{++}(1)$ are the Fourier harmonics in the leptonic tensor. Their 
explicit expressions can be found in \cite{Belitsky:2008bz}.  Therefore, Using 
the $\alpha_{i}$ factors, one can obtain in a totally model-independent way 
$\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ from fitting the 
experimental $A_{LU}$ as a function of $\phi$ for given values of $Q^2$, 
$x_{B}$, and $t$.

$A_{LU}$ can be simplified in terms of the collected number of events in each 
beam-helicity state ($N^{+}$, $N^{-}$) as:
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
\end{equation}
where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number 
of DVCS events detected with positive and negative electron helicity with 
respect to the beam direction. The statistical uncertainty of $A_{LU}$ is
\begin{equation}
   \sigma_{A_{LU}} = \frac{1}{P_{B}} \sqrt{ \frac{1 - (P_{B}A_{LU})^{2}}{N}}
\end{equation}
where $N (N^{+} + N^{-}) $ is the total number of measured events.

Due to our limited statistics only, a two-dimensional binning is carried out in 
this work. The strongest dependence of $A_{LU}$ is on the azimuthal angle 
($\phi$). Thus, the coherent measured ranges of $Q^{2}$, $x_{B}$ and $t$ are 
binned statistically into three bins. Then, the identified DVCS events in each 
bin are binned into nine bins in $\phi$. Therefore, we are left
with $Q^{2}$-$\phi$ bins integrated over the full ranges of $x_{B}$ and $t$, 
$x_{B}$-$\phi$ bins integrated over $Q^{2}$ and $t$, and $t$-$\phi$ bins 
integrated over $Q^{2}$ and $x_{B}$.

Figure \ref{fig:alu} presents the coherent $A_{LU}$ for the three
sets of two-dimensional bins. The asymmetries are fitted with the form of
equation \ref{eq:A_LU-coh}, where the real and the imaginary part of the CFF
$\mathcal{H}_{A}$ are the free parameters in the fit. Figure \ref{fig:alu90} 
shows the $Q^2$, $x_{B}$, and $-t$-dependencies of the fitted $A_{LU}$ signals 
at $\phi$~=~90$^{\circ}$. The $x_{B}$ and $-t$-dependencies are compared to 
theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. Their model relies on the impulse approximation and uses 
advanced spectral function of the nuclei to calculate the nuclear GPDs and then 
the observables. The calculations were carried out at slightly different 
kinematics than ours but provide already some guidance. The experimental 
results appear to have larger asymmetries compared to the calculations.  These 
differences may arise from nuclear effects which are not taken into account in 
the model, such as long-range interactions. Our measurements also agree with 
those of HERMES, considering their large uncertainties.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU.pdf}
\caption{The coherent $A_{LU}$ as a function of $\phi$ in
   $Q^{2}$(top panel), $x_{B}$ (middle panel), and $-t$ (bottom panel) bins.  
   The error bars represent the statistical uncertainties. The bluish-gray 
   bands represent the systematic uncertainties, including the normalisation 
systematic uncertainties. The red curves represent fits in the form of equation 
\ref{eq:A_LU-coh}.}
\label{fig:alu}
\end{figure}

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU_90.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $-t$-dependencies (right) of
   the coherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
   \cite{HERMES_BSA}, the colored curves represent theoretical calculations 
from \cite{simonetta_2}.}
\label{fig:alu90}
\end{figure}

As has been advertised previously, the $^4$He CFF $\mathcal{H}_A$ can be 
extracted from fitting the experimentally measured coherent $A_{LU}$ in a 
totally model independent way, which is not the case of nucleon targets. For 
the later, four CFFs exist and extracting them is always made by making 
limitations according some theoretical models and by neglecting some CFFs 
\cite{Jo:2015ema}. Figure \ref{fig:CFF_HA} presents our extracted imaginary and 
real parts of the CFF $\mathcal{H}_A$ as function of the kinematical variable 
($Q^{2}$, $x_B$,$-t$), and compared to some theoretical calculations.

@@

We display in figure \ref{fig:CFF_HA} calculations for $\mathcal{H}_A$ from 
three GPD models: On-shell, Convolution, and off-shell models. In the On-shell 
model \cite{Vadim_priv}, a nucleus is assumed to be composed of 
non-relativistic non-interacting nucleons, and these nucleons interact 
independently with the probe. For the nucleons, the GPDs are modeled according 
to the dual parametrization \cite{Guzey:2006xi}. In the Convolution model, the 
same assumption has been made for the nucleus, while the nucleon GPDs were 
extracted from the VGG model, which is based on the double distributions ansatz 
\cite{DD_model}. The Off-shell model \cite{GonzalezHernandez:2012jv} relies on 
the impulse approximation also, but uses advanced spectral function of the 
nuclei that accounts for all configurations of the final nuclear system and the 
binding effects between the nucleons.

@@

The incoherent DVCS channel 
measurement from the same data set in in preparation and will reported in 
another publication. 
%Acknowledgments

@@

\begin{thebibliography}{99}

@@

>>>>

A wealth of information on the quantum chromodynamics (QCD) lies in the 
internal structure of hadrons. In the recent past, the development of the 
generalized parton distributions (GPDs) framework has offered the possibility
to obtain new information about the momentum and spatial degrees of 
freedom of the quark and gluons inside hadrons 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
transverse plane for partons carrying a certain longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep}.

The main access to GPDs is through the measurement of deep virtual Compton 
scattering (DVCS), i.e. the hard exclusive electroproduction of a real photon. 
While other processes are known to be sensitive to GPDs, the measurement of the
DVCS is considered as the cleanest probe and has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
[Should we cite less publications on the topic or a review?]
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN. The vast majority of these measurements was focused on the study of the 
proton structure and allow the extraction of the tomography of the nucleon,
for details on the formalism see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}.
This framework is also applicable to nuclei, giving access to completely new 
information about the nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
The study of the 3D structure of the nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

@@

%DVCS selection
To identify the coherent DVCS events, we first select events where one 
electron, one $^4$He and at least one photon are detected in the final state. 
Electrons are identified by using fiducial cuts and detecting a good
signals in all the sub-detectors of the base line CLAS (drift chambers, 
Cherenkov counters, electromagnetic calorimeter, and time of flight 
scintillators). The $^4$He tracks are identified with fiducial, 
timing and track quality cuts in the RTPC detector. In addition,
we apply a vertex matching cut to make sure the electron and the helium
nuclei originate from the same place. The photons are detected either
in the IC or the CLAS electromagnetic calorimeter, note that even though the 
DVCS reaction has only one real photon in the final state, 
events with more than one good photon are not discarded at this stage. This is 
motivated by the fact that soft photons are likely to be produced in random 
coincidences, but cannot be mistaken for DVCS photons which are always at high
energies ($>2$ GeV). So, the most energetic photon is always considered as 
the DVCS photon candidate.

The main backgroud to the measurement of DVCS is the coherent $\pi^{0}$ 
production. Therefore, we remove events where a $\pi^{0}$ can be identified 
by invariant mass reconstruction of two photons.  To ensure that the 
interaction occurs at the partonic level and that the DVCS handbag diagram is 
applicable we select events with $Q^{2}>1~[GeV^{2}/c^{2}]$. The exclusivity of 
the events is obtained by applying a set of cuts on the following kinematic 
variables: the co-planarity angle ($\Delta \phi$), the missing energy, the 
missing mass squared, the missing transverse momentum, the missing mass 
squared of the $e'^4He'$ system and the angle ($\theta$) between the measured 
photon and the missing momentum of the $e'^4He'$ system. The most relevant of 
these cuts are presented in Figure~\ref{fig:kin-cuts}, these are 3$\sigma$ 
cuts except for the missing energy that appears to be too large and for which 
we reduced the cut window to [-0.45,0.5] GeV. After these requirements, we 
have about 3500 events left, Figure \ref{fig:kin-coverage} presents their
kinematic distributions in ($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
\caption{Four of the six coherent DVCS exclusivity cuts. The black 
distributions represent the coherent DVCS events candidate. The shaded 
distributions represent the events which passed all the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied exclusivity 
cuts. The distributions from left to right and from top to bottoms are: $\Delta 
\phi$, missing energy, missing mass squared and the 
cone angle ($\theta$) between the measured and the calculated photons.}
\label{fig:kin-cuts}
\end{figure}

\begin{figure}[tb]
\hspace{-0.45cm}
\includegraphics[width=9.0cm]{figs/Q2_xB_t_Coh.pdf}
\caption{Coherent DVCS event distributions for $Q^{2}$ as a function of 
$x_{B}$ (left) and $Q^{2}$ as a function of $-t$ (right) after the 
exclusivity cuts.}
\label{fig:kin-coverage}
\end{figure}

We identified two main background to our measurement, the accidental 
coincidences and the exclusive $\pi^0$ production. The accidental events have 
particles coming from different events, we estimate their  contribution
to 4.1\% of our sample. We evaluated this contribution by selecting events 
passing all our cuts but with an electron and an helium originating from different 
vertices. Regarding the $\pi^0$ production, it can easily be mistaken with DVCS when 
one of the two photons of the $\pi^0$ decay is produced at low energy in the 
laboratory frame and remain undetected. To estimate the importance of this 
background, we developed an event generator calibrated on the experimental yield 
of exclusive $\pi^0$ measured by our experiment. We used this generator together 
with a GEANT3 simulation of our detection system to estimate the ratio between
the number of $\pi^0$ events where the two photons are detected and those that 
would be mistaken for DVCS. This ratio is then multiplied by the measured yield 
of exclusive $\pi^0$ events to correct the DVCS data. Depending on the bins, we
found contaminations of 2 to 4\%. The study of systematics errors showed that the main 
contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
large binning size (5.1\%) [Is that right to add it here?]. However, added quadratically, these 
errors sum up to about 10\%, which always remain significantly smaller than the 
statistical errors.

%asymmetries
Several observables related to DVCS are of interest, in this work we focus 
only on the beam-spin asymmetry. This  
observable is measurable using a polarized lepton beam on an unpolarized target 
(U). It is convenient to use the beam-spin asymmetry
because most of the experimental normalization and acceptance issues cancel out 
in the asymmetry ratio. It is defined in terms of the cross sections as:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross 
section for a positive (negative) beam helicity. Experimentally, $A_{LU}$ 
can be expressed in terms of the collected number of events in each 
beam-helicity state ($N^{+}$, $N^{-}$) as:
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
\end{equation}
where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number 
of DVCS events detected with positive and negative electron helicity with 
respect to the beam direction.

To interpret the DVCS, one has to keep in mind that this reaction is 
indistinguishable from the Bethe-Heitler (BH) process, where the final photon 
is emitted either from the incoming or the outgoing leptons. At leading twist 
and leading order, the deeply virtual photon production cross section is 
composed of a BH, a DVCS, and an interference terms. The amplitudes of the 
three terms can be approximated as a finite sum of Fourier harmonics as shown 
for the nucleon in \cite{Belitsky:2001ns} and for the spinless targets in 
\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on these calculations, the 
beam-spin asymmetry ($A_{LU}$) can then be expressed as:
\small
\begin{equation}
\begin{split}
A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
 \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
\label{eq:A_LU-coh}
\end{split}
\end{equation}
\normalsize
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$. 
$\phi$ is the azimuthal angle between the ($e$,$e'$) and 
($\gamma^{*}$,$^4$He$'$) planes. The $\alpha_{i}$'s are $\phi$-dependent 
kinematical factors that depend on the nuclear form factor ($F_{A}(t)$) and the 
independent variables $Q^2$, $x_{B}$ and $t$. These factors are expressed as:
\small
\begin{eqnarray}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2}
\end{eqnarray}
\normalsize
Where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$ is the $^4$He mass, 
$\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the Bethe-Heitler
propagators. The factors: $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and
$s_1^{INT}$ are the Fourier coefficients of the BH, $S{++}(1)$, $C_{++}(0)$, 
and $C_{++}(1)$ are the Fourier harmonics in the leptonic tensor. The 
explicit expressions of these terms can be found in \cite{Belitsky:2008bz}. 
We see that using the $\sin(\phi)$ and $\cos(\phi)$ contributions, it is 
possible to extract 
$\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ from the beam spin
asymmetry.

Due to our limited statistics, we only bin  our data 
 on the azimuthal angle ($\phi$) and either one of the kinemtical variables 
$Q^{2}$, $x_{B}$ and $t$. Figure \ref{fig:alu} presents the $A_{LU}$ for the three
sets of binning. The asymmetries are fitted with the form of
equation \ref{eq:A_LU-coh}, where the real and the imaginary part of the CFF
$\mathcal{H}_{A}$ are the free parameters of the fit. Figure \ref{fig:alu90} 
shows the $Q^2$, $x_{B}$, and $-t$-dependencies of the fitted $A_{LU}$ signals 
at $\phi$~=~90$^{\circ}$. The $x_{B}$ and $-t$-dependencies are compared to 
the theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. Their model relies on the impulse approximation and uses 
advanced spectral function of the nuclei. The calculations are at slightly different 
kinematics than ours but provide some guidance. The experimental 
results appear to have larger asymmetries than the calculations. These 
differences may arise from nuclear effects which are not taken into account in 
the model, such as long-range interactions.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU.pdf}
\caption{The coherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and 
   $-t$ bins (bottom panel).  
   The error bars represent the statistical uncertainties. The gray 
   bands represent the systematic uncertainties, including the normalisation 
   uncertainties. The red curves are the results of our fits with the form of 
   equation \ref{eq:A_LU-coh}.}
\label{fig:alu}
\end{figure}

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU_90.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $-t$-dependencies (right) of
   the $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
   \cite{HERMES_BSA}, the colored curves represent theoretical calculations 
   from \cite{simonetta_2}.}
\label{fig:alu90}
\end{figure}

@@

We display in figure \ref{fig:CFF_HA} our extraction of the $^4$He CFF 
$\mathcal{H}_A$ together with theoretical calculations from two models 
labeled: convolution, and off-shell models. In the convolution 
model \cite{Vadim_priv}, the nucleus is assumed to be composed of 
non-relativistic non-interacting nucleons, and these nucleons interact 
independently with the probe. The convolution/dual model is based on nucleon GPDs from 
the dual parametrization \cite{Guzey:2006xi}, the convolution/VGG uses nucleon GPDs  
from the VGG model, which is based on the double distributions ansatz 
\cite{DD_model}. The Off-shell model \cite{GonzalezHernandez:2012jv} relies on 
impulse approximation and uses advanced spectral function of the 
nuclei that accounts for all configurations of the final nuclear system and the 
binding effects between the nucleons.
[These need to be renamed on the figure, it does not make sense to call differently
models that are identical. We should also request the projections from Vadim
model: hep-ph/0509158.]

@@

The incoherent DVCS channel 
measurement from the same data set in in preparation and will reported in 
another publication.

[order biblio]

%Acknowledgments

@@

\begin{thebibliography}{99}
\bibitem{Mueller:1998fv} 
D. Mueller, D. Robaschik, B. Geyer, F.M. Dittes and J. Horejsi,
Fortsch.\ Phys. {\bf 42}, 101 (1994).

\bibitem{Ji:1996ek} 
X.D. Ji,
Phys.\ Rev.\ Lett. {\bf 78}, 610 (1997).

\bibitem{Ji:1996nm} 
X.D. Ji,
Phys.\ Rev.\ D {\bf 55}, 7114 (1997).

\bibitem{Radyushkin:1996nd}
A.V. Radyushkin,
Phys.\ Lett.\  B {\bf 380}, 417 (1996).

\bibitem{Radyushkin:1997ki} 
A.V. Radyushkin,
Phys.\ Rev.\ D {\bf 56}, 5524 (1997).

@@

\bibitem{Goeke:2001tz}
K. Goeke, M.V. Polyakov and M. Vanderhaeghen,
Prog.\ Part.\ Nucl.\ Phys. {\bf 47}, 401 (2001).

\bibitem{Diehl:2003ny}
M. Diehl,
Phys.\ Rept.  {\bf 388}, 41 (2003).

\bibitem{Ji:2004gf}
X.D. Ji,
Ann.\ Rev.\ Nucl.\ Part.\ Sci. {\bf 54}, 413 (2004).

\bibitem{Belitsky:2005qn}
A.V. Belitsky and A.V. Radyushkin,
Phys.\ Rept. {\bf 418}, 1 (2005).

\bibitem{Boffi:2007yc} 
S. Boffi and B. Pasquini,
Riv.\ Nuovo Cim. {\bf 30}, 387 (2007).

\bibitem{Guidal:2013rya} 
M.~Guidal, H.~Moutarde and M.~Vanderhaeghen,
Rept.\ Prog.\ Phys.\  {\bf 76}, 066202 (2013).

\bibitem{Dupre:2015jha} 
  R.~Dupr\'e and S.~Scopetta,
  Eur.\ Phys.\ J.\ A {\bf 52}, no. 6, 159 (2016)

\bibitem{Hen:2016kwk} 
  O.~Hen, G.~A.~Miller, E.~Piasetzky and L.~B.~Weinstein,
  arXiv:1611.09748 [nucl-ex].

\bibitem{Norton:2003cb} 
  P.~R.~Norton,
  Rept.\ Prog.\ Phys.\  {\bf 66}, 1253 (2003).

\bibitem{Geesaman:1995yd} 
  D.~F.~Geesaman, K.~Saito and A.~W.~Thomas,
  Ann.\ Rev.\ Nucl.\ Part.\ Sci.\  {\bf 45}, 337 (1995).
